---
title: "pol_appendix_figs"
format: html
editor: visual
---

```{r}
library(ggplot2)
library(haven)
library(tidyverse)
library(patchwork)
library(fixest)
library(ggraph)
library(igraph)
library(ggfittext)
library(patchwork)
library(ggpubr)
library(scales)
#library(jsonlite)
library(readxl)
library(arrow)
library(tidyr)
#library(gt)  
library(dplyr) 
```

```{r}
make_candidate_ts <- function(df, labels, output_path,
                              width = 9, height = 6) {
  colnames(df)[1] <- "word"

  df_long <- df %>%
    pivot_longer(-word, names_to = "date", values_to = "count") %>%
    left_join(labels %>% dplyr::select(word = rep, info, analog), by = "word") %>%
    filter(info == "Candidate", !is.na(analog)) %>%
    mutate(week = floor_date(as.Date(date), unit = "week")) %>%
    group_by(week, analog) %>%
    summarise(total = sum(count, na.rm = TRUE), .groups = "drop")

  p <- ggplot(df_long, aes(x = week, y = total, color = analog)) +
    geom_line(linewidth = 0.5) +
    scale_x_date(
      limits = as.Date(c("2014-01-01", "2025-12-31")),
      date_breaks = "1 year",
      date_labels = "%Y"
    ) +
    labs(title = "Candidate Mentions Over Time", x = "Date", y = "Word Occurrences", color = "Candidate") +
    theme_classic() +
    theme(
      legend.position        = c(0.58, 0.78),
      legend.justification   = c("left", "top"),
      legend.background      = element_rect(fill = "white", color = "black", linewidth = 0.4),
      legend.margin          = margin(4, 6, 4, 6),
      legend.key.height      = unit(0.85, "lines"),
      legend.key.size        = unit(0.85, "lines"),
      legend.spacing.y       = unit(0.1, "cm"),
    )
  ggsave(output_path, plot = p, width = width, height = height, dpi = 300, units = "in")
  return(p)
}

make_candidate_ts(read_csv("candidate_counts.csv"), labels, "candidates.png")
```

### Robustness check / over-dispersion 
* Note that the this currently doesn't work b/c need to feed data in, plan to hook it all up when which figures in appendix are finalized * 
Estimated dispersion was θ = 0.6, indicating substantial overdispersion relative to Poisson. As a robustness check, we re-estimated the model with a fixed-effects Poisson specification with the same two-way clustering; coefficients were qualitatively unchanged, with somewhat larger point estimates as expected when overdispersed observations are not downweighted. We report the negative binomial estimates as the primary specification.
```{r}
summary(m)$theta   # the dispersion parameter; should be a positive finite number
summary(m)$nobs    # number of observations used in fit
m_pois <- fepois(
  count ~ phase + i(phase, is_partisan, ref = "off_cycle") | word,
  offset  = ~log(total_posts),
  data    = at,
  cluster = ~word + week
)
summary(m_pois)
```